---
title: "IST 687 Project Group 1"
subtitle: "Catherine Devine, Yodit Ayalew, Lauren Foltz, Jack Harris"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: paper
---

```{r libraries}
#Install Packages
#install.packages("flexdashboard")

#Install Libraries
library(flexdashboard)
library(gdata)
library(moments)
library(ggplot2)
library(ggmap)
library(zipcode)
```

```{r data}
#Read Data
DAPCancerEvents <- data.frame(read.xls("data/DAP_cancer_events_hosp.xls"),stringsAsFactors=FALSE)
#head(DAPCancerEvents)
#str(DAPCancerEvents)
#summary(DAPCancerEvents)
```

```{r clean}
#Clean data
##Remove first row (NA data)
DAPCancerEvents <- DAPCancerEvents[-1,]
##Remove last row (aggregate United States data)
DAPCancerEvents <- DAPCancerEvents[-939,]
##Remove columns 7 and 8 (confidence interval data)
DAPCancerEvents <- DAPCancerEvents[,-7:-8]
##Remove columns 8 and 9 (confidence interval data)
DAPCancerEvents <- DAPCancerEvents[,-8:-9]
##Remove columns 9 and 10 (confidence interval data)
DAPCancerEvents <- DAPCancerEvents[,-9:-10]
##Remove columns 10 and 11 (confidence interval data)
DAPCancerEvents <- DAPCancerEvents[,-10:-11]
##Remove columns 11 and 12 (confidence interval data)
DAPCancerEvents <- DAPCancerEvents[,-11:-12]
##Remove columns 12 and 13 (confidence interval data)
DAPCancerEvents <- DAPCancerEvents[,-12:-13]
##Remove columns 13 and 14 (confidence interval data)
DAPCancerEvents <- DAPCancerEvents[,-13:-14]
##Remove columns 14 and 15 (confidence interval data)
DAPCancerEvents <- DAPCancerEvents[,-14:-15]
##Remove columns 15 and 16 (confidence interval data)
DAPCancerEvents <- DAPCancerEvents[,-15:-16]
##Remove columns 18 and 19 (confidence interval data)
DAPCancerEvents <- DAPCancerEvents[,-16:-17]
##Remove columns 19 and 20 (confidence interval data)
DAPCancerEvents <- DAPCancerEvents[,-17:-18]
namelist <- c("Provider ID","Hospital","City","State",
              "Deaths","% died in hospital",
              "% admitted last month","Hospital days last month",
              "% admitted ICU last month","ICU days last month",
             "% life sust treatment last month","% chemo last 2 weeks",
              "% hospice last month","hospice days last month",
              "% hospice last 3 days","% > 10 physicians last 6 months")
names(DAPCancerEvents) <- namelist
#View(DAPCancerEvents)
#str(DAPCancerEvents)
```

```{r clean1}
#Define Numberize function to convert to numerics and remove spaces and commas
Numberize<-function(inputVector){
  inputVector<-gsub(",","",inputVector)
  inputVector<-gsub(" ","",inputVector)
  return(as.numeric(inputVector)) }

#Convert columns 5 (Deaths) through 16 (% >10 physicians last 6 months) to numbers using Numberize, as well as remove spaces
DAPCancerEvents$Deaths <- Numberize(DAPCancerEvents$Deaths)
DAPCancerEvents$`% died in hospital` <- Numberize(DAPCancerEvents$`% died in hospital`)
DAPCancerEvents$`% admitted last month` <- Numberize(DAPCancerEvents$`% admitted last month`)
DAPCancerEvents$`Hospital days last month` <- Numberize(DAPCancerEvents$`Hospital days last month`)
DAPCancerEvents$`% admitted ICU last month` <- Numberize(DAPCancerEvents$`% admitted ICU last month`)
DAPCancerEvents$`ICU days last month` <- Numberize(DAPCancerEvents$`ICU days last month`)
DAPCancerEvents$`% life sust treatment last month` <- Numberize(DAPCancerEvents$`% life sust treatment last month`)
DAPCancerEvents$`% chemo last 2 weeks` <- Numberize(DAPCancerEvents$`% chemo last 2 weeks`)
DAPCancerEvents$`% hospice last month` <- Numberize(DAPCancerEvents$`% hospice last month`)
DAPCancerEvents$`hospice days last month` <- Numberize(DAPCancerEvents$`hospice days last month`)
DAPCancerEvents$`% hospice last 3 days` <- Numberize(DAPCancerEvents$`% hospice last 3 days`)
DAPCancerEvents$`% > 10 physicians last 6 months` <- Numberize(DAPCancerEvents$`% > 10 physicians last 6 months`)
#str(DAPCancerEvents)
```

```{r subset data}
#subset Deaths for descriptive function and remove NAs
DAPCancerEvents5 <- DAPCancerEvents[,5]
DAPCancerEvents5 <- na.omit(DAPCancerEvents5)
#subset % died in hospital for descriptive function and remove NAs
DAPCancerEvents6 <- DAPCancerEvents[,6]
DAPCancerEvents6 <- na.omit(DAPCancerEvents6)
#subset % admitted last month for descriptive function and remove NAs
DAPCancerEvents7 <- DAPCancerEvents[,7]
DAPCancerEvents7 <- na.omit(DAPCancerEvents7)
#subset % hospital days last month for descriptive function and remove NAs
DAPCancerEvents8 <- DAPCancerEvents[,8]
DAPCancerEvents8 <- na.omit(DAPCancerEvents8)
#subset % admitted last month for descriptive function and remove NAs
DAPCancerEvents9 <- DAPCancerEvents[,9]
DAPCancerEvents9 <- na.omit(DAPCancerEvents9)
#subset % ICU days last month for descriptive function and remove NAs
DAPCancerEvents10 <- DAPCancerEvents[,10]
DAPCancerEvents10 <- na.omit(DAPCancerEvents10)
#subset % life sustaining treatment last month for descriptive function and remove NAs
DAPCancerEvents11 <- DAPCancerEvents[,11]
DAPCancerEvents11 <- na.omit(DAPCancerEvents11)
#subset % chemo last 2 weeks for descriptive function and remove NAs
DAPCancerEvents12 <- DAPCancerEvents[,12]
DAPCancerEvents12 <- na.omit(DAPCancerEvents12)
#subset % hospice last month for descriptive function and remove NAs
DAPCancerEvents13 <- DAPCancerEvents[,13]
DAPCancerEvents13 <- na.omit(DAPCancerEvents13)
#subset hospice days last  month for descriptive function and remove NAs
DAPCancerEvents14 <- DAPCancerEvents[,14]
DAPCancerEvents14 <- na.omit(DAPCancerEvents14)
#subset % hospice last 3 days for descriptive function and remove NAs
DAPCancerEvents15 <- DAPCancerEvents[,15]
DAPCancerEvents15 <- na.omit(DAPCancerEvents15)
#subset % >10 physicians last 6 months for descriptive function and remove NAs
DAPCancerEvents16 <- DAPCancerEvents[,16]
DAPCancerEvents16 <- na.omit(DAPCancerEvents16)

```

```{r colors}
#Color Palettes (sourced from http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/)
#Palette of colors for use in graphs
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

```{r functions}
#functions
#create functions to generate descriptive statistics, maps and graphs
descriptive <- function(x){
  print(paste("Mean:",mean(x)))
  print(paste("Median:",median(x)))
  print(paste("Standard Deviation:",sd(x)))
  print(paste("Skewness:",skewness(x)))
  print(paste("Kurtosis:",kurtosis(x)))
  hist(x,main=paste(title),xlab=title,col = cbbPalette[4])
}

xlabel <- "State"
xlabel1 <- "Hospital"

byhospital <- function(x){
    hospitalmap <- ggplot(DAPCancerEvents,aes(x=DAPCancerEvents$Hospital,y=col,colour=col)) + geom_point(colour=cbbPalette[8]) +   ggtitle(title1) 
    hospitalmap <- hospitalmap + labs(x=xlabel1,y=title)
    hospitalmap <- hospitalmap + theme_classic()
  hospitalmap
}

bystate <- function(x){
  statemap <- ggplot(DAPCancerEvents,aes(x=DAPCancerEvents$state,y=col,
                           colour=col)) + geom_point(colour=cbbPalette[6]) + 
                          ggtitle(title2)
  statemap <- statemap +labs(x=xlabel,y=title)
  statemap <- statemap + theme_classic()
  statemap
}

#create function to generate maps
mapvariable <- function(x){
    us <- map_data("state")
    map <- ggplot(DAPCancerEvents,aes(map_id=statename))  
    map <- map + geom_map(map=us,aes(fill=col))
    map <- map + labs(x=NULL, y=NULL)
    map <- map + expand_limits(x=
          us$long, y=us$lat) 
    map <- map + coord_map()
    map <- map + ggtitle(title2)
    map <- map + theme_classic()
    map
}
```


```{r state data}
#state data
#load zipcode data
data(zipcode)
zipcode1 <- tolower(zipcode$state)
#add statename field
DAPCancerEvents$state <- tolower(DAPCancerEvents$State)
DAPCancerEvents <- DAPCancerEvents[,-4]
#DAPCancerEvents
```

```{r state data 1}
#create dataframe with state abbreviations and names
statescd <- as.data.frame(state.abb,state.name)
#take rownames and create new field statename from them
statescd$statename <- rownames(statescd)
#set both columns to lowercase
statescd$state.abb <- tolower(statescd$state.abb)
statescd$state <- statescd$state.abb
statescd$statename <- tolower(statescd$statename)
#create dataframe that merges statecd and zip.df by state
DAPCancerEvents <- merge(DAPCancerEvents,statescd, by="state")
#DAPCancerEvents
```


```{r linear regression}
#Linear Regression for all models with correlation greater than |0.5|

#regression model for predicting % died in hospital by percentage hospital days last month
#as the variable
DAPCancerEvents.lm = lm(formula=DAPCancerEvents$`% died in hospital`~DAPCancerEvents$`Hospital days last month`,
              data=DAPCancerEvents)
DAPCancerEvents.model <- summary(DAPCancerEvents.lm)
#summary(DAPCancerEvents.lm)

#paste("adjusted r squared:",DAPCancerEvents.model$adj.r.squared) #adj r squared
```


Summary
===================================== 

This reflects an analysis of the DAP Cancer Events dataset. This dataset contains 938 rows (one row per hospital), and 12 attributes for each hospital.  

We've conducted the following analysis for each attribute  
- defined descriptive statistics  
- histogram  
- scatterplot of data by hospital  
- scatterplot of data by state  
- map data  

In addition, we've run a correlation analysis and then a linear regression model for all correlations greater than |0.5|  



Analysis
===================================== 
Column {.tabset .tabset-fade}
-------------------------------------

### **Deaths**
#### Chart 1
```{r Deaths}
#generate descriptive statistics and histograms for each variable
col <- DAPCancerEvents$Deaths
title <- "Deaths"
title1 <- "Deaths by Hospital"
title2 <- "Deaths by State"
#Call descriptive function
descriptive(DAPCancerEvents5)
```

#### Chart 2
```{r Deaths1}
byhospital(col)
```

#### Chart 3
```{r Deaths2}
bystate(col)
```

#### Chart 4
```{r Deaths3}
mapvariable(col)
```


### **% Died in Hospital**
#### Chart 1
```{r Died in Hospital}
#generate descriptive statistics and histograms for each variable
col <- DAPCancerEvents$`% died in hospital`
title <- "Percent Died in Hospital"
title1 <- "Percent Died in Hospital by Hospital"
title2 <- "Percent Died in Hospital by State"
descriptive(DAPCancerEvents6)
```

#### Chart 2
```{r Died in Hospital 1}
byhospital(col)
```

#### Chart 3
```{r r Died in Hospital 2}
bystate(col)
```

#### Chart 4
```{r Died in Hospital 3}
mapvariable(col)
```

### **% Admitted Last Month of Life**
#### Chart 1
```{r Admitted Last Month}
#generate descriptive statistics and histograms for each variable
col <- DAPCancerEvents$`% admitted last month`
title <- "Percent Admitted to Hospital in Last Month of Life"
title1 <- "Percent Admitted to Hospital in Last Month of Life - by Hospital"
title2 <- "Percent Admitted to Hospital in Last Month of Life - by State"
descriptive(DAPCancerEvents7)
```

#### Chart 2
```{r Admitted Last Month 1}
byhospital(col)
```

#### Chart 3
```{r Admitted Last Month 2}
bystate(col)
```

#### Chart 4
```{r Admitted Last Month 3}
mapvariable(col)
```

### **Hospital Days Last Month of Life**
#### Chart 1
```{r Hospital Days}
#generate descriptive statistics and histograms for each variable
col <- DAPCancerEvents$`Hospital days last month`
title <- "Hospital Days Last Month of Life"
title1 <- "Hospital Days Last Month of Life - by Hospital"
title2 <- "Hospital Days Last Month - by State"
descriptive(DAPCancerEvents8)
```

#### Chart 2
```{r Hospital Days 1}
byhospital(col)
```

#### Chart 3
```{r Hospital Days 2}
#### Chart 3
bystate(col)
```

#### Chart 4
```{r Hospital Days 3}
#### Chart 4
mapvariable(col)
```


### **% Admitted to ICU Last Month of Life**
#### Chart 1
```{r ICU}
#generate descriptive statistics and histograms for each variable
col <- DAPCancerEvents$`% admitted ICU last month`
title <- "Percent Admitted to ICU Last Month of Life"
title1 <- "Percent Admitted to ICU Last Month of Life - by Hospital"
title2 <- "Percent Admitted to ICU Last Month of Life - by State"
descriptive(DAPCancerEvents9)
```

#### Chart 2
```{r ICU 1}
byhospital(col)
```

#### Chart 3
```{r ICU 2}
bystate(col)
```

#### Chart 4
```{r ICU 3}
mapvariable(col)
```


### **ICU Days Last Month of Life**
#### Chart 1
```{r ICU days}
#generate descriptive statistics and histograms for each variable
col <- DAPCancerEvents$`ICU days last month`
title <- "ICU Days Last Month of Life"
title1 <- "ICU Days Last Month of Life - by Hospital"
title2 <- "ICU Days Last Month of Life - by State"
descriptive(DAPCancerEvents10)
```

#### Chart 2
```{r ICU Days 1}
byhospital(col)
```

#### Chart 3
```{r ICU Days 2}
bystate(col)
```

#### Chart 4
```{r ICU Days 3}
mapvariable(col)
```

### **% receiving life sustaining treatment last month of life**
#### Chart 1
```{r Life Sust}
#generate descriptive statistics and histograms for each variable
col <- DAPCancerEvents$`% life sust treatment last month`
title <- "Percent Life Sustaining Treatment Last Month of Life"
title1 <- "Percent Life Sustaining Treatment Last Month of Life - by Hospital"
title2 <- "Percent Life Sustaining Treatment Last Month of Life - by State"
descriptive(DAPCancerEvents11)
```

#### Chart 2
```{r Life Sust 1}
byhospital(col)
```

#### Chart 3
```{r Life Sust 2}
bystate(col)
```

#### Chart 4
```{r Life Sust 3}
mapvariable(col)
```


### **% receiving chemotherapy last 2 weeks of life**
#### Chart 1
```{r Chemo}
#generate descriptive statistics and histograms for each variable
col <- DAPCancerEvents$`% chemo last 2 weeks`
title <- "Percent Chemo Last 2 Weeks of Life"
title1 <- "Percent Chemo Last 2 Weeks of Life - by Hospital"
title2 <- "Percent Chemo Last 2 Weeks of Life - by State"
descriptive(DAPCancerEvents12)
```

#### Chart 2
```{r Chemo 1}
byhospital(col)
```

#### Chart 3
```{r Chemo 2}
bystate(col)
```

#### Chart 4
```{r Chemo 3}
mapvariable(col)
```


### **% Hospice last month of life**
#### Chart 1
```{r Hospice}
#generate descriptive statistics and histograms for each variable
col <- DAPCancerEvents$`% hospice last month`
title <- "Percent Hospice Last Month of Life"
title1 <- "Percent Hospice Last Month of Life - by Hospital"
title2 <- "Percent Hospice Last Month of Life - by State"
descriptive(DAPCancerEvents13)
```

#### Chart 2
```{r Hospice 1}
byhospital(col)
```

#### Chart 3
```{r Hospice 2}
bystate(col)
```

#### Chart 4
```{r Hospice 3}
mapvariable(col)
```

### **Hospice Days Last Month of Life**
#### Chart 1
```{r Hospice Days}
#generate descriptive statistics and histograms for each variable
col <- DAPCancerEvents$`hospice days last month`
title <- "Hospice Days Last Month of Life"
title1 <- "Hospice Days Last Month of Life - by Hospital"
title2 <- "Hospice Days Last Month of Life - by State"
descriptive(DAPCancerEvents14)
```

#### Chart 2
```{r Hospice Days 1}
byhospital(col)
```

#### Chart 3
```{r Hospice Days 2}
bystate(col)
```

#### Chart 4
```{r Hospice Days 3}
mapvariable(col)
```

### **% Hospice Last 3 Days of Life**
#### Chart 1
```{r Hospice Days last 3}
#generate descriptive statistics and histograms for each variable
col <- DAPCancerEvents$`% hospice last 3 days`
title <- "% Hospice Last 3 Days of Life"
title1 <- "% Hospice  Last 3 Days of Life - by Hospital"
title2 <- "% Hospice  Last 3 Days of Life - by State"
descriptive(DAPCancerEvents15)
```

#### Chart 2
```{r Hospice Days last 3 1}
byhospital(col)
```

#### Chart 3
```{r Hospice Days last 3 2}
bystate(col)
```

#### Chart 4
```{r Hospice Days last 3 3}
mapvariable(col)
```

### **% saw more than 10 physicians last 6 months of life**
#### Chart 1
```{r physicians}
#generate descriptive statistics and histograms for each variable
col <- DAPCancerEvents$`% > 10 physicians last 6 months`
title <- "> 10 Physicians Seen in Last 6 Months of Life"
title1 <- "> 10 Physicians Seen in Last 6 Months of Life - by Hospital"
title2 <- "> 10 Physicians Seen in Last 6 Months of Life - by State"
descriptive(DAPCancerEvents16)
```

#### Chart 2
```{r physicians 1}
byhospital(col)
```

#### Chart 3
```{r physicians 2}
bystate(col)
```

#### Chart 4
```{r physicians 3}
mapvariable(col)
```

Correlation
===================================== 
```{r correlation}
#install.packages("ggcorrplot")
library("ggcorrplot")
correlationdata <- DAPCancerEvents[,5:16]
DAP.cor<- round(cor(correlationdata,use="complete.obs"),4)
#Note used "complete.obs" rather than "everything"
#head(DAP.cor[, 1:6])
ggcorrplot(DAP.cor, hc.order=TRUE, type="lower")

```

Linear Regression 
===================================== 

Row {data-height=650}
-------------------------------------
#### predicting % hospice last month given % died in hospital
```{r linear regression 1}
#Linear Regression

#regression model for predicting % hospice last month considering % died in hospital
#as the variable
DAPCancerEvents.lm = lm(formula=DAPCancerEvents$`% hospice last month`~DAPCancerEvents$`% died in hospital`,
              data=DAPCancerEvents)
DAPCancerEvents.model <- summary(DAPCancerEvents.lm)
#summary(DAPCancerEvents.lm)

paste ("Adjusted r squared=", DAPCancerEvents.model$adj.r.squared)

```

#### predicting % died in hospital given number of hospice days last month
```{r linear regression 2}
#Linear Regression

#regression model for predicting % died in hospital considering hospice days last month. 
#as the variable
DAPCancerEvents.lm = lm(formula=DAPCancerEvents$`% died in hospital`~DAPCancerEvents$`hospice days last month`,
              data=DAPCancerEvents)
DAPCancerEvents.model <- summary(DAPCancerEvents.lm)
#summary(DAPCancerEvents.lm)

paste ("Adjusted r squared=", DAPCancerEvents.model$adj.r.squared)

```

#### predicting hospital days last month given % admitted last month
```{r linear regression 3}

#Linear Regression
#regression model for predicting hospital days last month considering % admitted last month. 
#as the variable
DAPCancerEvents.lm = lm(formula=DAPCancerEvents$`Hospital days last month`~DAPCancerEvents$`% admitted last month`,
              data=DAPCancerEvents)
DAPCancerEvents.model <- summary(DAPCancerEvents.lm)
#summary(DAPCancerEvents.lm)

paste ("Adjusted r squared=", DAPCancerEvents.model$adj.r.squared)

```

#### predicting hospice days last month given % admitted last month
```{r linear regression 4}
#Linear Regression

#regression model for predicting hospice days last month given % admitted last month
#as the variable
DAPCancerEvents.lm = lm(formula=DAPCancerEvents$`hospice days last month`~`% admitted last month`,
              data=DAPCancerEvents)
DAPCancerEvents.model <- summary(DAPCancerEvents.lm)
#summary(DAPCancerEvents.lm)

paste ("Adjusted r squared=", DAPCancerEvents.model$adj.r.squared)
```

#### predicting ICU days last month given % admitted ICU last month
```{r linear regression 5}
#Linear Regression

#regression model for predicting ICU days last month considering % admitted ICU last month
#as the variable
DAPCancerEvents.lm = lm(formula=DAPCancerEvents$`ICU days last month`~DAPCancerEvents$`% admitted ICU last month`,
              data=DAPCancerEvents)
DAPCancerEvents.model <- summary(DAPCancerEvents.lm)
#summary(DAPCancerEvents.lm)

paste ("Adjusted r squared=", DAPCancerEvents.model$adj.r.squared)
```

#### predicting hospice days last month given % hospice last month
```{r linear regression 6}
#Linear Regression

#regression model for predicting hospice days last month given percentage in hospice last month
#as the variable
DAPCancerEvents.lm = lm(formula=DAPCancerEvents$`hospice days last month`~DAPCancerEvents$`% hospice last month`,
              data=DAPCancerEvents)
DAPCancerEvents.model <- summary(DAPCancerEvents.lm)
#summary(DAPCancerEvents.lm)

paste ("Adjusted r squared=", DAPCancerEvents.model$adj.r.squared)
```

#### predicting % hospice last 3 days given % hospice last month
```{r linear regression 7}
#Linear Regression

#regression model for predicting % hospice last 3 days considering % hospice last month
#as the variable
DAPCancerEvents.lm = lm(formula=DAPCancerEvents$`% hospice last 3 days`~DAPCancerEvents$`% hospice last month`,
              data=DAPCancerEvents)
DAPCancerEvents.model <- summary(DAPCancerEvents.lm)
#summary(DAPCancerEvents.lm)

paste ("Adjusted r squared=", DAPCancerEvents.model$adj.r.squared)
```

#### predicting % died in hospital given hospital, hospice days and percentage hospice days last month
```{r linear regression 8}
#Linear Regression

#regression model for predicting % died in hospital considered both Hospital days last month and hospice days last month and % hospice last month
#as the variable
DAPCancerEvents.lm = lm(formula=DAPCancerEvents$`% died in hospital`~DAPCancerEvents$`Hospital days last month`+
                          DAPCancerEvents$`% hospice last month`+DAPCancerEvents$`hospice days last month`,
              data=DAPCancerEvents)
DAPCancerEvents.model <- summary(DAPCancerEvents.lm)
#summary(DAPCancerEvents.lm)

paste ("Adjusted r squared=", DAPCancerEvents.model$adj.r.squared)


```

#### predicting % died in hospital given state
```{r linear regression 9}
#Linear Regression

#regression model for predicting % died in hospital considered state
#as the variable
DAPCancerEvents.lm = lm(formula=DAPCancerEvents$`% died in hospital`~DAPCancerEvents$state,
              data=DAPCancerEvents)
DAPCancerEvents.model <- summary(DAPCancerEvents.lm)
#summary(DAPCancerEvents.lm)

paste ("Adjusted r squared=", DAPCancerEvents.model$adj.r.squared)
```

#### predicting % died in hospital given city
```{r linear regression 10}
#Linear Regression

#regression model for predicting % died in hospital considering city
#as the variable
DAPCancerEvents.lm = lm(formula=DAPCancerEvents$`% died in hospital`~DAPCancerEvents$City,
              data=DAPCancerEvents)
DAPCancerEvents.model <- summary(DAPCancerEvents.lm)
#summary(DAPCancerEvents.lm)

paste ("Adjusted r squared=", DAPCancerEvents.model$adj.r.squared)
```

#### predicting % died in hospital given city and state
```{r linear regression 11}
#Linear Regression

#regression model for predicting % died in hospital considering city and state
#as the variable
DAPCancerEvents.lm = lm(formula=DAPCancerEvents$`% died in hospital`~DAPCancerEvents$City+DAPCancerEvents$state,
              data=DAPCancerEvents)
DAPCancerEvents.model <- summary(DAPCancerEvents.lm)
#summary(DAPCancerEvents.lm)

paste ("Adjusted r squared=", DAPCancerEvents.model$adj.r.squared)
```


Linear Models 
===================================== 
Column {.tabset .tabset-fade}
-------------------------------------
### **Plot LM 1**
```{r linear model 1}
g <- ggplot(DAPCancerEvents, 
            aes(x= DAPCancerEvents$`% died in hospital`,y= DAPCancerEvents$`% hospice last month`))
g <- g + geom_point()
g <- g + stat_smooth(method="lm", col = "red")
g <- g + ggtitle("Linear Model 1: PREDICT % hospice last month BASED ON % died in hospital")
g <- g+labs(x="% died in hospital", y="% hospice last month")
g
```

### **Plot LM 2**
```{r linear model 2}
g <- ggplot(DAPCancerEvents,aes(x= DAPCancerEvents$`hospice days last month`,
                              y= DAPCancerEvents$`% died in hospital`)) +geom_point()
g<-g+stat_smooth(method="lm", col = "red")
g <- g + ggtitle("Linear Model 2: PREDICT % died in hospital BASED ON Hospice Days Last Month")
g <- g+labs(x="Hospice days last month", y="% died in hospital")
g
```

### **Plot LM 3**
```{r linear model 3}
g <- ggplot(DAPCancerEvents,aes(x= DAPCancerEvents$`% admitted last month`, 
                                y= DAPCancerEvents$`Hospital days last month`)) + geom_point()
g<-g+stat_smooth(method="lm", col = "red")
g<-g+ggtitle("Linear Model 3: PREDICT Hospital Days Last Month BASED ON % admitted last month")
g <- g+labs(x="% admitted last month", y="Hospital days last month")
g
```

### **Plot LM 4**
```{r linear model 4}
g<-ggplot(DAPCancerEvents,aes(x= DAPCancerEvents$`% admitted last month`, y= DAPCancerEvents$`hospice days last month` ))+geom_point()
g<-g+stat_smooth(method="lm", col = "red")
g<-g+ggtitle("Linear Model 4: PREDICT Hospice Days Last Month based on % admitted last month")
g <- g+labs(x="% admitted last month", y="Hospice days last month")
g
```


### **Plot LM 5**
```{r linear model 5}
g<-ggplot(DAPCancerEvents,aes(x= DAPCancerEvents$`% admitted ICU last month`, y= DAPCancerEvents$`ICU days last month` ))+geom_point()
g<-g+stat_smooth(method="lm", col = "red")
g<-g+ggtitle("Linear Model 5: PREDICT ICU days last month BASED ON % admitted ICU last month.")
g<-g+labs(x="% admitted ICU last month", y="ICU days last month")
g
```

### **Plot LM 6**
```{r linear model 6}
g<-ggplot(DAPCancerEvents,aes(x= DAPCancerEvents$`% hospice last month`, y= DAPCancerEvents$`hospice days last month` ))+geom_point()
g<-g+stat_smooth(method="lm", col = "red")
g<-g+ggtitle("Linear Model 6: PREDICT hospice days last month based on % hospice last month")
g <- g+labs(x="% hospice last month", y="Hospice days last month")
g
```

### **Plot LM 7**
```{r linear model 7}
g<-ggplot(DAPCancerEvents,aes(x= DAPCancerEvents$`% hospice last month`, y= DAPCancerEvents$`% hospice last 3 days` ))+geom_point()
g<-g+stat_smooth(method="lm", col = "red")
g<-g+ggtitle("Linear Model 7: PREDICT hospice last 3 days of life based on % hospice last month")
g <- g+labs(x="% hospice last 3 days", y="% hospice last month")
g
```



